---
title: "Myproject"
author: "Sandeep Grover"
date: "23/09/2020"
output:
  md_document: 
     variant: markdown_github
    
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown {#nextsteps .emphasized}

Here is a link to [SLACK] (https://ikeabworkspace.slack.com/archives/C01BC64V1FC)

The objective of my **project** is to __compare__ group A vs. group B.

This would enable us to *discover* new _treatments_.

THe name of current project is `ClinicalABC`.



```{r examples, echo=TRUE}
2+2
mean(c(1,2,3,4,5))


```
#########################################
1. Introduction
    a. Disease
        i. Prevalence
        ii. Causes
        iii. Treatment
    b. Objective
        i. Markers
2. Methods
    a. Regression
3. Results
    a. Descriptive 
    b. Main results
    c. Secondary results
########################################
    
> Parkinson's disease is one of the most 
> common neurodegenerative diseases.
>
> 1. The disease is characterized by degeneration of
> 2. The disease has an delayed age of onset
>
> > above 60

#######################################
```{r packages, warning=FALSE, include=FALSE}
library(myfirstrepository)
library(tidyverse)
# for general work
library(data.table)
# for reading file
library(table1)
# for table creation
```

```{r}

knitr::kable(head(rawdata))
table1::label(rawdata$age_onset) <- "Age at onset of PD"
rawdata$atc_fam_mutation <- factor(rawdata$atc_fam_mutation, levels = c(1,0),  labels =  c("Yes", "No"))
#table1::label(rawdata$gender) <- "Gender"
table1::label(rawdata$pd_duration) <- "Duration of PD"
table1::label(rawdata$GBA_mutation) <- "Presence of GBA mutation"
table1::label(rawdata$LRKK2_mutation) <- "Presence of LRKK2 mutation"
table1::label(rawdata$atc_fam_mutation) <- "Presence of ATC mutation"

#rawdata$gender <- factor(rawdata$gender, levels = c(1,2),  labels =  c("Male", "Female"))

descriptivetable <- table1(~ age_onset + pd_duration + GBA_mutation + LRKK2_mutation + atc_fam_mutation, data = rawdata)

descriptivetable
#descriptivetable <- table1(~ age_onset + pd_duration + GBA_mutation + LRKK2_mutation + atc_fam_mutation| gender, data = rawdata)

#tables <- loadWorkbook("tables.xlsx", create = T)
#createSheet(tables, name = "tables")
#writeWorksheet(tables, descriptivetable, sheet = "tables")
#saveWorkbook(tables, file = "tables.xlsx")
```


```{r directories, eval=FALSE, warning=FALSE, include=FALSE}
project.dir <-  "C:/Users/grover/OneDrive - bwstaff/myfirstrepository/myfirstrepository"
data.dir <- sprintf("%s/data", project.dir)
code.dir <- sprintf("%s/code", project.dir)
text.dir <- sprintf("%s/text", project.dir)
figure.dir <- sprintf("%s/figure", project.dir)
report.dir <-  sprintf("%s/report", project.dir)
table.dir <-  sprintf("%s/table", project.dir)
slides.dir <- sprintf("%s/slides", project.dir)
setwd(project.dir)
dir.create(data.dir)
dir.create(code.dir)
dir.create(text.dir)
dir.create(figure.dir)
dir.create(report.dir)
dir.create(table.dir)
dir.create(slides.dir)
##########
clinical.fn <- sprintf("%s/all_studies.txt", data.dir)
#if(!file.exists("all_studies.txt")){
#dowload.file("dropbox/allstudies.txt", "all_studies.txt")
#}
# Manual download or copy to folder
```

## Including Plots

$$ Y = \beta_0 + \beta_1*X $$




You can also embed plots, for example:

#```{r data cleaning, echo=FALSE}
head(rawdata)
rawdata %>%  slice(40:50) %>% 
  select(starts_with("age")) %>% 
  filter(age_study > 80) %>% 
  rename (age = age_study) %>% 
  mutate(age = age/10) %>% 
  group_by() %>% summarize() %>%
  merge()
  table1()
  write_csv()%>%
  #function() %>%
  to_lower() %>%
  arrange(desc()) %>%
  count()
  
  # Go ahead and save this data in your package, name it as cleandata.
  # cleandata()
  # 
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
